RBE/CS549 Project: Boat Tracking/Detection

### 2017-12-14 paper/main.tex
Add diaereses to spellings of naive

\subsection{Naive K-Means Classifier}
We initially started with a basic two-class k-means classifier in order to
observe how well it would perform.  The classifier was trained on the first
image in the video sequence, and the L2 distance to the two cluster centers was
used to classify each pixel in subsequent frames.  Surprisingly enough, the
2-class k-means classifier worked relatively robustly on the videos that we
provided the algorithm, as show in figure \ref{fig:kmeans}.  The water pixels
are mostly labeled as one class, and pixels that not water are mostly labeled as
another class with a little bit of misclassification noise.  The boat and it's
wake are clearly labeled as potential obstacles to track, which is what we want.
The land areas are labeled as water pixels, but for our implementation we want
to ignore tracking the land anyways. There is a slight bit of noise in the water
reflections towards the right side of figure \ref{fig:kmeans}, but this naive
method still provides very useful information.

@@

\begin{figure}
\includegraphics[width=7.8cm]{hsv_kmeans2_orig}
\includegraphics[width=8.5cm]{hsv_kmeans2_result}
\centering
\caption{Naive K-Means Classifier Results}
\label{fig:kmeans}
\end{figure}

>>>>

\subsection{Na\"ive K-Means Classifier}
We initially started with a basic two-class k-means classifier in order to
observe how well it would perform.  The classifier was trained on the first
image in the video sequence, and the L2 distance to the two cluster centers was
used to classify each pixel in subsequent frames.  Surprisingly enough, the
2-class k-means classifier worked relatively robustly on the videos that we
provided the algorithm, as show in figure \ref{fig:kmeans}.  The water pixels
are mostly labeled as one class, and pixels that not water are mostly labeled as
another class with a little bit of misclassification noise.  The boat and it's
wake are clearly labeled as potential obstacles to track, which is what we want.
The land areas are labeled as water pixels, but for our implementation we want
to ignore tracking the land anyways. There is a slight bit of noise in the water
reflections towards the right side of figure \ref{fig:kmeans}, but this na\"ive
method still provides very useful information.

@@

\begin{figure}
\includegraphics[width=7.8cm]{hsv_kmeans2_orig}
\includegraphics[width=8.5cm]{hsv_kmeans2_result}
\centering
\caption{Na\"ive K-Means Classifier Results}
\label{fig:kmeans}
\end{figure}
